---
title: "Conference Poster Template"
subtitle: "For Professional Meetings and Academic Conferences"
author:
  - name: "Presenter Name"
    affiliation: "Department, Institution"
    email: "presenter@institution.edu"
  - name: "Co-Presenter Name"
    affiliation: "Department, Institution"
date: last-modified
format:
  poster-typst:
    size: "42x30" 
    orientation: "landscape"
    poster-authors: "Presenter Name, Co-Presenter Name"
    departments: "Department, Institution"
    institution-logo: "../../styles/logo.png"
    institution-url: "institution.edu"
    footer-text: "Conference Name, Location, Date"
    footer-color: "#4169E1"
    header-color: "#4169E1"
    sectitle-color: "#4169E1"
    columns: 4
    fontsize: 28px
    sectitle-fontsize: 38px
    title-fontsize: 54px
    self-contained: true
---

# Conference Information

**Event**: [Full Conference Name]  
**Location**: [City, State/Country]  
**Date**: [Conference Dates]  
**Session**: [Poster Session ID/Number]  
**Track**: [Conference Track/Theme]

# Abstract

[Include a brief abstract of your poster presentation here - 150-200 words summarizing the purpose, methods, results, and conclusions.]

# Introduction

## Context

- [Brief overview of the field or topic]
- [Current state of knowledge]
- [Gap or problem being addressed]

## Objective

[Clearly state the objective or purpose of this work]

# Methods

## Design

[Overview of study design or approach]

## Materials

- [Key materials or equipment]
- [Software or tools used]
- [Data sources]

## Procedure

1. [Step 1 of your methodology]
2. [Step 2 of your methodology]
3. [Step 3 of your methodology]

# Results

## Main Findings

[Present your key results in a clear, visually appealing manner]

```{r}
#| echo: false
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "Figure 1: Key Results"
# Insert code for primary visualization here
```

## Secondary Results

[Additional results that support your main findings]

```{r}
#| echo: false
#| fig-width: 7
#| fig-height: 5
#| fig-cap: "Figure 2: Supporting Results"
# Insert code for secondary visualization here
```

# Implications

## Field Impact

- [How these findings contribute to the field]
- [Theoretical implications]
- [Practical applications]

## Broader Impact

- [Relevance to industry, policy, or society]
- [Potential benefits or applications]

# Conclusions

## Summary

- [Brief summary of key findings]
- [Main takeaway points]
- [Answer to research question]

## Future Work

- [Next steps in this research]
- [Unanswered questions]
- [Planned extensions]

# Acknowledgments

[Funding sources]  
[Contributors]  
[Support staff or resources]

# Contact Information

**Presenter Name**  
Email: presenter@institution.edu  
ORCID: [ORCID ID]  
Website: institution.edu/presenter

**Scan for additional information:**

```{r qrcode, echo=FALSE}
#| eval: false
# For including a QR code
#library(qrcode)
#qr <- qr_code("https://yourwebsite.com/research")
#plot(qr)
```
