---
title: "Academic Poster Template"
subtitle: "For Research Conferences and Symposiums"
author:
  - name: Author Name
    affiliation: University Department
    email: author@university.edu
    orcid: 0000-0000-0000-0000
  - name: Co-Author Name
    affiliation: University Department
    email: coauthor@university.edu
date: last-modified
format:
  poster-typst:
    size: "36x24"
    poster-authors: "Author Name, Co-Author Name"
    departments: "University Department"
    institution-logo: "../../_extensions/SU_primary logo/RGB/Gold and maroon RGB/Png/SU corporate_horizontal_without_slogan_RGB-01.png"
    institution-url: "university.edu"
    footer-text: "Conference Name, Location, Date"
    footer-color: "#b79962"
    header-color: "#61223b"
    sectitle-color: "#61223b"
    columns: 3
    font-family: "Montserrat"
    sectitle-font-family: "Josefin Sans"
    self-contained: true
bibliography: ../../refs.bib
---

# Introduction

Research posters are a common way to present ongoing or completed research at academic conferences. They provide a visual summary of your work and serve as a conversation starter with other researchers.

This template provides a standard layout for academic posters with sections for introduction, methods, results, and conclusion.

# Background

- Summarize relevant literature
- Identify knowledge gaps
- State the research question
- Explain the significance of your work

# Methods

## Study Design
- Type of study (e.g., experimental, observational)
- Participant selection
- Inclusion/exclusion criteria

## Data Collection
- Measures and instruments
- Procedures
- Timeframe

## Analysis
- Statistical methods
- Software used
- Model specifications
- Validation approaches

# Results

## Primary Findings

```{r}
#| echo: false
#| fig-cap: "Key Results Figure 1"
# Code to generate plot
plot(1:10, 1:10, type="l", xlab="Variable X", ylab="Outcome Y")
```

## Secondary Analyses

```{r}
#| echo: false
#| tbl-cap: "Summary Statistics"
# Code to generate table
data.frame(
  Variable = c("Age", "Gender (F)", "Education (years)", "Income ($)"),
  Mean = c(45.2, 0.51, 16.2, 62500),
  SD = c(12.3, 0.50, 2.3, 15400),
  Range = c("18-72", "0-1", "12-22", "25k-120k")
)
```

# Discussion

## Interpretation of Findings
- Explain the meaning of key results
- Connect to existing literature
- Address unexpected findings

## Limitations
- Sample limitations
- Methodological constraints
- Potential biases

## Implications
- Theoretical implications
- Practical applications
- Clinical relevance

# Conclusion

- Summarize key findings
- Highlight main contributions
- Suggest directions for future research

# References

::: {#refs}
:::

# Acknowledgments

- Funding sources
- Technical assistance
- Data access
- Participant contributions

# Contact Information

**Author Name**  
University Department  
email@university.edu  
Website: author-website.edu  
