---
title: "Progress Report: {{project_name}}"
subtitle: "{{meeting_type}} Update - {{date_range}}"
author:
  - name: {{author_name}}
    email: {{author_email}}
    affiliations: {{affiliation}}
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    embed-resources: true
    theme: cosmo
    css: ../../styles/meeting-report.css
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
    geometry:
      - top=1in
      - bottom=1in
      - left=1in
      - right=1in
  docx:
    toc: true
    number-sections: true
    highlight-style: github
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)

# Load required libraries
library(knitr)
library(dplyr)
library(ggplot2)
library(plotly)
library(DT)
```

# Executive Summary

## Meeting Overview

**Meeting Details:**
- **Type:** {{meeting_type}}
- **Date:** {{meeting_date}}
- **Previous Meeting:** {{previous_meeting_date}}
- **Period Covered:** {{days_elapsed}} days ({{start_date}} to {{end_date}})
- **Project Phase:** {{current_phase}}
- **Report Prepared By:** {{author_name}}

## Key Highlights

:::{.callout-note}
## At a Glance
- **Overall Progress:** {{overall_progress}}% complete
- **Major Milestones:** {{milestones_completed}}/{{total_milestones}} completed
- **Critical Issues:** {{critical_issues}} active
- **Team Velocity:** {{team_velocity}} ({{velocity_trend}})
- **Budget Status:** {{budget_status}}
- **Timeline Status:** {{timeline_status}}
:::

### Major Achievements This Period

1. **{{achievement_1}}** - {{achievement_1_detail}}
2. **{{achievement_2}}** - {{achievement_2_detail}}
3. **{{achievement_3}}** - {{achievement_3_detail}}

### Critical Issues Requiring Attention

1. **{{critical_issue_1}}** - Priority: {{priority_1}}
2. **{{critical_issue_2}}** - Priority: {{priority_2}}
3. **{{critical_issue_3}}** - Priority: {{priority_3}}

# Detailed Progress Report

## Accomplishments Since Last Meeting

### {{category_1}}

**Completed Items:**
- {{completed_1_1}} - {{completion_date_1_1}}
- {{completed_1_2}} - {{completion_date_1_2}}
- {{completed_1_3}} - {{completion_date_1_3}}

**Key Outcomes:**
- {{outcome_1_1}}
- {{outcome_1_2}}
- {{outcome_1_3}}

**Metrics:**
- Tasks Completed: {{tasks_completed_1}}/{{tasks_planned_1}}
- Quality Score: {{quality_score_1}}/10
- Timeline Adherence: {{timeline_adherence_1}}%

### {{category_2}}

**Completed Items:**
- {{completed_2_1}} - {{completion_date_2_1}}
- {{completed_2_2}} - {{completion_date_2_2}}
- {{completed_2_3}} - {{completion_date_2_3}}

**Key Outcomes:**
- {{outcome_2_1}}
- {{outcome_2_2}}
- {{outcome_2_3}}

**Metrics:**
- Tasks Completed: {{tasks_completed_2}}/{{tasks_planned_2}}
- Quality Score: {{quality_score_2}}/10
- Timeline Adherence: {{timeline_adherence_2}}%

### {{category_3}}

**Completed Items:**
- {{completed_3_1}} - {{completion_date_3_1}}
- {{completed_3_2}} - {{completion_date_3_2}}
- {{completed_3_3}} - {{completion_date_3_3}}

**Key Outcomes:**
- {{outcome_3_1}}
- {{outcome_3_2}}
- {{outcome_3_3}}

**Metrics:**
- Tasks Completed: {{tasks_completed_3}}/{{tasks_planned_3}}
- Quality Score: {{quality_score_3}}/10
- Timeline Adherence: {{timeline_adherence_3}}%

## Progress Dashboard

```{r progress-dashboard}
# Create sample progress data
progress_data <- data.frame(
  Category = c("{{category_1}}", "{{category_2}}", "{{category_3}}", "Overall"),
  Planned = c({{tasks_planned_1}}, {{tasks_planned_2}}, {{tasks_planned_3}}, {{total_tasks_planned}}),
  Completed = c({{tasks_completed_1}}, {{tasks_completed_2}}, {{tasks_completed_3}}, {{total_tasks_completed}}),
  Percentage = c({{progress_1}}, {{progress_2}}, {{progress_3}}, {{overall_progress}})
)

# Create progress visualization
ggplot(progress_data, aes(x = Category)) +
  geom_col(aes(y = Planned, fill = "Planned"), alpha = 0.6, width = 0.6) +
  geom_col(aes(y = Completed, fill = "Completed"), width = 0.6) +
  geom_text(aes(y = Completed + 0.5, label = paste0(Percentage, "%")), 
            vjust = 0, fontweight = "bold") +
  scale_fill_manual(values = c("Planned" = "#e0e0e0", "Completed" = "#2E86AB")) +
  labs(title = "Progress by Category",
       subtitle = "Tasks Completed vs Planned",
       x = "Category",
       y = "Number of Tasks",
       fill = "Status") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Issues and Troubleshooting

## Problems Encountered

### {{issue_1_category}} Issues

#### {{issue_1_title}}

**Severity:** {{issue_1_severity}}  
**Status:** {{issue_1_status}}  
**Date Identified:** {{issue_1_date}}  
**Owner:** {{issue_1_owner}}

**Problem Description:**
{{issue_1_description}}

**Impact Analysis:**
- **Technical Impact:** {{issue_1_tech_impact}}
- **Timeline Impact:** {{issue_1_timeline_impact}}
- **Budget Impact:** {{issue_1_budget_impact}}
- **Stakeholder Impact:** {{issue_1_stakeholder_impact}}

**Root Cause Analysis:**
1. **Primary Cause:** {{issue_1_primary_cause}}
2. **Contributing Factors:** 
   - {{issue_1_factor_1}}
   - {{issue_1_factor_2}}
   - {{issue_1_factor_3}}

**Resolution Approach:**
1. **Immediate Actions:** {{issue_1_immediate_actions}}
2. **Short-term Solutions:** {{issue_1_short_term}}
3. **Long-term Prevention:** {{issue_1_long_term}}

**Current Status:** {{issue_1_current_status}}

#### {{issue_2_title}}

**Severity:** {{issue_2_severity}}  
**Status:** {{issue_2_status}}  
**Date Identified:** {{issue_2_date}}  
**Owner:** {{issue_2_owner}}

**Problem Description:**
{{issue_2_description}}

**Resolution Summary:**
{{issue_2_resolution}}

**Lessons Learned:**
- {{issue_2_lesson_1}}
- {{issue_2_lesson_2}}
- {{issue_2_lesson_3}}

## Issue Resolution Process

```{mermaid}
graph TD
    A[Issue Identified] --> B{Severity Assessment}
    B -->|Critical| C[Immediate Response Team]
    B -->|High| D[Priority Assignment]
    B -->|Medium/Low| E[Standard Process]
    C --> F[Emergency Mitigation]
    D --> G[Resource Allocation]
    E --> H[Analysis \u0026 Planning]
    F --> I[Root Cause Analysis]
    G --> I
    H --> I
    I --> J[Solution Development]
    J --> K[Implementation]
    K --> L[Testing \u0026 Validation]
    L --> M[Documentation]
    M --> N[Process Improvement]
```

## Troubleshooting Knowledge Base

### Common Issues and Solutions

| Issue Type | Frequency | Avg Resolution Time | Standard Solution |
|------------|-----------|---------------------|-------------------|
| {{issue_type_1}} | {{frequency_1}} | {{resolution_time_1}} | {{solution_1}} |
| {{issue_type_2}} | {{frequency_2}} | {{resolution_time_2}} | {{solution_2}} |
| {{issue_type_3}} | {{frequency_3}} | {{resolution_time_3}} | {{solution_3}} |

### Prevention Measures

1. **{{prevention_1}}** - {{prevention_1_description}}
2. **{{prevention_2}}** - {{prevention_2_description}}
3. **{{prevention_3}}** - {{prevention_3_description}}

# Team Performance and Notes

## Team Velocity and Capacity

```{r team-metrics}
# Team performance data
team_data <- data.frame(
  Week = 1:{{weeks_in_period}},
  Planned_Velocity = c({{planned_velocity_data}}),
  Actual_Velocity = c({{actual_velocity_data}}),
  Team_Capacity = c({{team_capacity_data}})
)

# Velocity trend chart
ggplot(team_data, aes(x = Week)) +
  geom_line(aes(y = Planned_Velocity, color = "Planned"), size = 1.2) +
  geom_line(aes(y = Actual_Velocity, color = "Actual"), size = 1.2) +
  geom_line(aes(y = Team_Capacity, color = "Capacity"), linetype = "dashed") +
  scale_color_manual(values = c("Planned" = "#2E86AB", "Actual" = "#A23B72", "Capacity" = "#F18F01")) +
  labs(title = "Team Velocity Trend",
       subtitle = "Planned vs Actual Velocity Over Time",
       x = "Week",
       y = "Story Points",
       color = "Metric") +
  theme_minimal()
```

## Individual Contributions

### Team Member Performance

```{r team-performance}
# Individual performance data
individual_data <- data.frame(
  Team_Member = c("{{member_1}}", "{{member_2}}", "{{member_3}}", "{{member_4}}"),
  Tasks_Completed = c({{member_1_tasks}}, {{member_2_tasks}}, {{member_3_tasks}}, {{member_4_tasks}}),
  Quality_Score = c({{member_1_quality}}, {{member_2_quality}}, {{member_3_quality}}, {{member_4_quality}}),
  Contribution_Percentage = c({{member_1_contrib}}, {{member_2_contrib}}, {{member_3_contrib}}, {{member_4_contrib}})
)

# Display as interactive table
datatable(individual_data, 
          options = list(pageLength = 10, searching = FALSE),
          caption = "Individual Team Member Performance") %>%
  formatPercentage(c('Contribution_Percentage'), 1) %>%
  formatRound(c('Quality_Score'), 1)
```

## Key Observations and Notes

### What Worked Well

1. **{{success_observation_1}}**
   - **Evidence:** {{success_evidence_1}}
   - **Impact:** {{success_impact_1}}
   - **Replication Strategy:** {{success_replication_1}}

2. **{{success_observation_2}}**
   - **Evidence:** {{success_evidence_2}}
   - **Impact:** {{success_impact_2}}
   - **Replication Strategy:** {{success_replication_2}}

### Areas for Improvement

1. **{{improvement_area_1}}**
   - **Current State:** {{current_state_1}}
   - **Desired State:** {{desired_state_1}}
   - **Action Plan:** {{action_plan_1}}
   - **Success Metrics:** {{success_metrics_1}}

2. **{{improvement_area_2}}**
   - **Current State:** {{current_state_2}}
   - **Desired State:** {{desired_state_2}}
   - **Action Plan:** {{action_plan_2}}
   - **Success Metrics:** {{success_metrics_2}}

### Process Improvements Implemented

1. **{{process_improvement_1}}**
   - **Rationale:** {{improvement_rationale_1}}
   - **Implementation Date:** {{implementation_date_1}}
   - **Early Results:** {{early_results_1}}

2. **{{process_improvement_2}}**
   - **Rationale:** {{improvement_rationale_2}}
   - **Implementation Date:** {{implementation_date_2}}
   - **Early Results:** {{early_results_2}}

# Next Steps and Action Plan

## Immediate Priorities (Next 1-2 Weeks)

### Priority 1: {{priority_1}}

**Objective:** {{priority_1_objective}}  
**Owner:** {{priority_1_owner}}  
**Due Date:** {{priority_1_due}}  
**Dependencies:** {{priority_1_dependencies}}

**Success Criteria:**
- {{priority_1_criteria_1}}
- {{priority_1_criteria_2}}
- {{priority_1_criteria_3}}

**Resource Requirements:**
- **Human Resources:** {{priority_1_hr}}
- **Technical Resources:** {{priority_1_tech}}
- **Budget:** {{priority_1_budget}}

**Risk Factors:**
- {{priority_1_risk_1}} (Probability: {{risk_1_prob}}, Impact: {{risk_1_impact}})
- {{priority_1_risk_2}} (Probability: {{risk_2_prob}}, Impact: {{risk_2_impact}})

### Priority 2: {{priority_2}}

**Objective:** {{priority_2_objective}}  
**Owner:** {{priority_2_owner}}  
**Due Date:** {{priority_2_due}}  
**Dependencies:** {{priority_2_dependencies}}

**Success Criteria:**
- {{priority_2_criteria_1}}
- {{priority_2_criteria_2}}
- {{priority_2_criteria_3}}

### Priority 3: {{priority_3}}

**Objective:** {{priority_3_objective}}  
**Owner:** {{priority_3_owner}}  
**Due Date:** {{priority_3_due}}  
**Dependencies:** {{priority_3_dependencies}}

**Success Criteria:**
- {{priority_3_criteria_1}}
- {{priority_3_criteria_2}}
- {{priority_3_criteria_3}}

## Medium-Term Goals (2-4 Weeks)

### Development Focus

1. **{{dev_goal_1}}**
   - **Timeline:** {{dev_timeline_1}}
   - **Milestones:** {{dev_milestones_1}}
   - **Resources:** {{dev_resources_1}}

2. **{{dev_goal_2}}**
   - **Timeline:** {{dev_timeline_2}}
   - **Milestones:** {{dev_milestones_2}}
   - **Resources:** {{dev_resources_2}}

### Quality Assurance Focus

1. **{{qa_goal_1}}**
   - **Testing Strategy:** {{qa_strategy_1}}
   - **Coverage Target:** {{qa_coverage_1}}
   - **Timeline:** {{qa_timeline_1}}

2. **{{qa_goal_2}}**
   - **Testing Strategy:** {{qa_strategy_2}}
   - **Coverage Target:** {{qa_coverage_2}}
   - **Timeline:** {{qa_timeline_2}}

## Risk Management

### Current Risk Register

```{r risk-matrix}
# Risk assessment data
risk_data <- data.frame(
  Risk = c("{{risk_1}}", "{{risk_2}}", "{{risk_3}}", "{{risk_4}}"),
  Probability = c("{{prob_1}}", "{{prob_2}}", "{{prob_3}}", "{{prob_4}}"),
  Impact = c("{{impact_1}}", "{{impact_2}}", "{{impact_3}}", "{{impact_4}}"),
  Mitigation = c("{{mitigation_1}}", "{{mitigation_2}}", "{{mitigation_3}}", "{{mitigation_4}}"),
  Owner = c("{{risk_owner_1}}", "{{risk_owner_2}}", "{{risk_owner_3}}", "{{risk_owner_4}}")
)

datatable(risk_data,
          options = list(pageLength = 10, scrollX = TRUE),
          caption = "Active Risk Register")
```

### Mitigation Strategies

1. **High-Priority Risks**
   - {{high_risk_mitigation_1}}
   - {{high_risk_mitigation_2}}

2. **Medium-Priority Risks**
   - {{medium_risk_mitigation_1}}
   - {{medium_risk_mitigation_2}}

3. **Monitoring and Review**
   - **Review Frequency:** {{risk_review_frequency}}
   - **Escalation Criteria:** {{escalation_criteria}}
   - **Communication Plan:** {{risk_communication_plan}}

# Dependencies and Blockers

## Current Dependencies

### External Dependencies

| Dependency | Provider | Expected Delivery | Status | Impact if Delayed |
|------------|----------|-------------------|--------|-------------------|
| {{dependency_1}} | {{provider_1}} | {{delivery_1}} | {{status_1}} | {{impact_1}} |
| {{dependency_2}} | {{provider_2}} | {{delivery_2}} | {{status_2}} | {{impact_2}} |
| {{dependency_3}} | {{provider_3}} | {{delivery_3}} | {{status_3}} | {{impact_3}} |

### Internal Dependencies

| Dependency | Owner | Required By | Status | Action Required |
|------------|-------|-------------|--------|-----------------|
| {{internal_dep_1}} | {{internal_owner_1}} | {{internal_due_1}} | {{internal_status_1}} | {{internal_action_1}} |
| {{internal_dep_2}} | {{internal_owner_2}} | {{internal_due_2}} | {{internal_status_2}} | {{internal_action_2}} |
| {{internal_dep_3}} | {{internal_owner_3}} | {{internal_due_3}} | {{internal_status_3}} | {{internal_action_3}} |

## Active Blockers

### Technical Blockers

1. **{{tech_blocker_1}}**
   - **Description:** {{tech_blocker_1_desc}}
   - **Impact:** {{tech_blocker_1_impact}}
   - **Resolution Plan:** {{tech_blocker_1_plan}}
   - **ETA:** {{tech_blocker_1_eta}}

2. **{{tech_blocker_2}}**
   - **Description:** {{tech_blocker_2_desc}}
   - **Impact:** {{tech_blocker_2_impact}}
   - **Resolution Plan:** {{tech_blocker_2_plan}}
   - **ETA:** {{tech_blocker_2_eta}}

### Process Blockers

1. **{{process_blocker_1}}**
   - **Description:** {{process_blocker_1_desc}}
   - **Impact:** {{process_blocker_1_impact}}
   - **Resolution Plan:** {{process_blocker_1_plan}}
   - **ETA:** {{process_blocker_1_eta}}

# Communication and Stakeholder Management

## Stakeholder Updates

### Communication Schedule

| Stakeholder Group | Next Update | Format | Key Messages | Owner |
|-------------------|-------------|--------|--------------|-------|
| {{stakeholder_1}} | {{update_date_1}} | {{format_1}} | {{message_1}} | {{owner_1}} |
| {{stakeholder_2}} | {{update_date_2}} | {{format_2}} | {{message_2}} | {{owner_2}} |
| {{stakeholder_3}} | {{update_date_3}} | {{format_3}} | {{message_3}} | {{owner_3}} |

### Key Messages by Audience

#### Executive Leadership
- **Progress Summary:** {{exec_progress}}
- **Critical Issues:** {{exec_issues}}
- **Resource Needs:** {{exec_resources}}
- **Timeline Update:** {{exec_timeline}}

#### Technical Teams
- **Technical Achievements:** {{tech_achievements}}
- **Upcoming Challenges:** {{tech_challenges}}
- **Integration Points:** {{tech_integration}}
- **Support Needed:** {{tech_support}}

#### Project Stakeholders
- **Milestone Updates:** {{stakeholder_milestones}}
- **Quality Metrics:** {{stakeholder_quality}}
- **User Impact:** {{stakeholder_impact}}
- **Feedback Requests:** {{stakeholder_feedback}}

# Meeting Planning

## Next Meeting Agenda

**Date:** {{next_meeting_date}}  
**Duration:** {{meeting_duration}}  
**Format:** {{meeting_format}}

### Planned Agenda Items

1. **Review of Action Items** ({{agenda_time_1}})
   - Follow-up on previous meeting action items
   - Status updates from owners

2. **{{agenda_item_1}}** ({{agenda_time_2}})
   - {{agenda_detail_1}}
   - **Presenter:** {{presenter_1}}
   - **Outcome:** {{outcome_1}}

3. **{{agenda_item_2}}** ({{agenda_time_3}})
   - {{agenda_detail_2}}
   - **Presenter:** {{presenter_2}}
   - **Outcome:** {{outcome_2}}

4. **{{agenda_item_3}}** ({{agenda_time_4}})
   - {{agenda_detail_3}}
   - **Presenter:** {{presenter_3}}
   - **Outcome:** {{outcome_3}}

5. **Risk and Issue Review** ({{agenda_time_5}})
   - Current risk status
   - New issues identification
   - Mitigation updates

6. **Next Steps and Action Items** ({{agenda_time_6}})
   - Assignment of new action items
   - Confirmation of timelines
   - Resource allocation decisions

### Pre-Meeting Preparation

**Required Preparation:**
- {{prep_item_1}} - Due: {{prep_due_1}} - Owner: {{prep_owner_1}}
- {{prep_item_2}} - Due: {{prep_due_2}} - Owner: {{prep_owner_2}}
- {{prep_item_3}} - Due: {{prep_due_3}} - Owner: {{prep_owner_3}}

**Materials to Review:**
- {{material_1}}
- {{material_2}}
- {{material_3}}

**Questions for Discussion:**
1. {{discussion_question_1}}
2. {{discussion_question_2}}
3. {{discussion_question_3}}

# Appendices

## Appendix A: Detailed Metrics

### Performance Metrics

```{r detailed-metrics}
# Detailed performance metrics
metrics_data <- data.frame(
  Metric = c("{{metric_name_1}}", "{{metric_name_2}}", "{{metric_name_3}}", "{{metric_name_4}}"),
  Target = c({{target_1}}, {{target_2}}, {{target_3}}, {{target_4}}),
  Current = c({{current_1}}, {{current_2}}, {{current_3}}, {{current_4}}),
  Previous = c({{previous_1}}, {{previous_2}}, {{previous_3}}, {{previous_4}}),
  Trend = c("{{trend_1}}", "{{trend_2}}", "{{trend_3}}", "{{trend_4}}")
)

datatable(metrics_data,
          options = list(pageLength = 10),
          caption = "Detailed Performance Metrics") %>%
  formatRound(c('Target', 'Current', 'Previous'), 2)
```

## Appendix B: Technical Details

### System Performance

- **Uptime:** {{system_uptime}}%
- **Response Time:** {{response_time}}ms (avg)
- **Error Rate:** {{error_rate}}%
- **Throughput:** {{throughput}} requests/second

### Code Quality Metrics

- **Code Coverage:** {{code_coverage}}%
- **Technical Debt:** {{technical_debt}} hours
- **Complexity Score:** {{complexity_score}}
- **Security Vulnerabilities:** {{security_vulns}}

## Appendix C: Resource Utilization

### Budget Tracking

| Category | Budgeted | Spent | Remaining | Utilization % |
|----------|----------|-------|-----------|---------------|
| {{budget_cat_1}} | ${{budget_1}} | ${{spent_1}} | ${{remaining_1}} | {{utilization_1}}% |
| {{budget_cat_2}} | ${{budget_2}} | ${{spent_2}} | ${{remaining_2}} | {{utilization_2}}% |
| {{budget_cat_3}} | ${{budget_3}} | ${{spent_3}} | ${{remaining_3}} | {{utilization_3}}% |

### Team Capacity

| Team Member | Allocated Hours | Actual Hours | Efficiency % | Availability |
|-------------|----------------|--------------|--------------|--------------|
| {{team_member_1}} | {{allocated_1}} | {{actual_1}} | {{efficiency_1}}% | {{availability_1}} |
| {{team_member_2}} | {{allocated_2}} | {{actual_2}} | {{efficiency_2}}% | {{availability_2}} |
| {{team_member_3}} | {{allocated_3}} | {{actual_3}} | {{efficiency_3}}% | {{availability_3}} |

---

**Report Generated:** `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`  
**Next Review:** {{next_review_date}}  
**Distribution:** {{distribution_list}}

:::{.callout-tip}
## Document Information
- **Template Version:** 1.0
- **Last Updated:** {{template_last_updated}}
- **Feedback:** {{feedback_contact}}
:::
