---
title: "Academic Presentation Template"
subtitle: "For Research Talks, Conferences, and Seminars"
format: 
  clean-revealjs:
    self-contained: true
    logo: "../../_extensions/SU_primary logo/RGB/Gold and maroon RGB/Png/SU corporate_horizontal_without_slogan_RGB-01.png"
html-math-method:
  method: mathjax
  url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
author:
  - name: Your Name
    orcid: 0000-0000-0000-0000
    email: your.email@institution.edu
    affiliations: Your Institution
date: last-modified
bibliography: ../../refs.bib
brand:
  color:
    primary: "#61223b"
    secondary: "#b79962"
    tertiary: "#005F61"
  typography:
    fonts:
      - family: Montserrat
        source: google
      - family: Josefin Sans
        source: google
      - family: Fira Code
        source: google
    base: Montserrat
    headings:
      family: Josefin Sans
      weight: semi-bold
    monospace:
      family: Fira Code
      size: 0.9em
---

## Introduction {background-color="#40666e"}

### Research Background

- Brief overview of the research field
- Highlight key gaps or challenges
- State the research question

### Literature Review

- Summarize existing work in 3-4 bullet points
- Highlight theoretical framework
- Identify methodological approaches in the literature

## Methodology {background-color="#40666e"}

### Research Design

- Describe your approach
- Define key variables or constructs
- State hypotheses (if applicable)

:::: {.columns}
::: {.column width="50%"}
#### Data Collection
- Source of data
- Sample size
- Inclusion/exclusion criteria
:::

::: {.column width="50%"}
#### Analysis Approach
- Statistical methods
- Software used
- Validation approaches
:::
::::

## Results {background-color="#40666e"}

### Key Findings

:::: {.columns}
::: {.column width="60%"}
```{r}
#| echo: false
#| fig-cap: "Example figure showing results"
# Your code to generate a plot would go here
# This is just a placeholder
plot(1:10, 1:10, type="l", xlab="X", ylab="Y")
```
:::

::: {.column width="40%"}
- Finding 1 with brief explanation
- Finding 2 with brief explanation
- Finding 3 with brief explanation
:::
::::

### Statistical Results

```{r}
#| echo: false
#| tbl-cap: "Regression Results"
# Code to generate a table would go here
# This is just a placeholder
data.frame(
  Variable = c("X1", "X2", "X3", "Constant"),
  Coefficient = c(0.56, 1.23, -0.41, 2.34),
  `Std. Error` = c(0.12, 0.18, 0.09, 0.22),
  `p-value` = c(0.001, 0.04, 0.06, "<0.001")
)
```

## Discussion {background-color="#40666e"}

### Interpretation

- Connect findings back to research question
- Compare with previous literature
- Highlight novel contributions

### Limitations

- Acknowledge key limitations
- Explain impact on findings
- Suggest improvements for future work

## Conclusion {background-color="#40666e"}

### Summary of Findings

- Recap key results
- Emphasize main contributions
- Connect to broader implications

### Future Directions

- Identify next steps
- Suggest extensions of current work
- Propose new research questions

## References {background-color="#40666e"}

::: {#refs}
:::

## Acknowledgments {background-color="#40666e"}

- Funding source(s)
- Collaborators and contributions
- Institutional support
- Contact information

## Appendix {background-color="#40666e"}

### Supplementary Materials

- Additional analyses
- Extended methodology details
- Access to data and code
