---
title: "Title of Experiment"
author: "Your Name"
date: "2025-05-25"
format: html
jupyter: true
# Add other formats as needed (pdf, docx, etc.)
# editor: visual
# bibliography: references.bib
# csl: your-style.csl
# Execute code on render
execute:
  echo: true
  warning: false
  message: false
---

# 1. Introduction and Objectives

Briefly describe the context, motivation, and objectives of your computational experiment.

- **Background:**
- **Research Question(s):**
- **Objectives:**

---

# 2. Experimental Design

Describe your experimental setup and plan.

- **Overview:**
- **Datasets/Source:**
- **Diagram/Flowchart:**
- **Dependencies and Environment:**
   - R/Python version:
   - Package versions:
   - Hardware:

---

# 3. Data Acquisition and Preprocessing

```{r}
# Download, import, or load your data here
```

- **Raw data inspection:**
- **Preprocessing steps:**
- **Summary statistics:**
- **Data partitioning (train/test/validation):**

---

# 4. Methods/Modeling

Describe and implement the computational methods or models.

- **Methods/Algorithms:**
- **Parameter settings:**
- **Implementation details:**
- **References:**

```{python}
# Example: Method implementation or model training
```

---

# 5. Experiment Execution

Document the actual running of experiments.

```{r}
# Run experiments, log outputs, record random seeds, etc.
```

- **Intermediate results:**
- **Troubleshooting:**

---

# 6. Results

Present and discuss your findings using tables, plots, and text interpretation.

```{python}
# Visualizations, summary tables, etc.
```

- **Statistical analysis:**
- **Comparison to baselines:**
- **Interpretation:**

---

# 7. Discussion

Discuss insights, limitations, and potential improvements.

- **Key findings:**
- **Limitations:**
- **Unexpected observations:**
- **Alternative approaches:**

---

# 8. Conclusions

Summarize main findings and outline next steps.

---

# 9. Reproducibility Checklist

- Instructions to rerun this notebook
- Environment/dependencies
- Random seeds/configuration
- Data access

---

# 10. References

<!-- List references here or use a .bib file -->

---

# 11. Appendix (Optional)

Additional code, figures, or supplementary information.
