---
title: "Title of Experiment"
author: "Your Name"
date: "2025-05-25"
format: html
jupyter: true
# Add other formats as needed (pdf, docx, etc.)
# editor: visual
# bibliography: references.bib
# csl: your-style.csl
# Execute code on render
execute:
  echo: true
  warning: false
  message: false
---

# 1. Introduction and Objectives

Briefly describe the context, motivation, and objectives of your computational experiment.

- **Background:**
- **Research Question(s):**
- **Objectives:**

---

# 2. Experimental Design

Describe your experimental setup and plan.

- **Overview:**
- **Datasets/Source:**
- **Diagram/Flowchart:**
- **Dependencies and Environment:**
   - R/Python version:
   - Package versions:
   - Hardware:

---

# 3. Data Acquisition and Preprocessing

```{r}
# Download, import, or load your data here
```

- **Raw data inspection:**
- **Preprocessing steps:**
- **Summary statistics:**
- **Data partitioning (train/test/validation):**

---

# 4. Methods/Modeling

Describe and implement the computational methods or models.

- **Methods/Algorithms:**
- **Parameter settings:**
- **Implementation details:**
- **References:**

```{python}
# Example: Method implementation or model training
```

---

# 5. Experiment Execution

Document the actual running of experiments.

```{r}
# Run experiments, log outputs, record random seeds, etc.
```

- **Intermediate results:**
- **Troubleshooting:**

---

# 6. Results

Present and discuss your findings using tables, plots, and text interpretation.

```{python}
# Visualizations, summary tables, etc.
```

- **Statistical analysis:**
- **Comparison to baselines:**
- **Interpretation:**

---

# 7. Discussion

Discuss insights, limitations, and potential improvements.

- **Key findings:**
- **Limitations:**
- **Unexpected observations:**
- **Alternative approaches:**

---

# 8. Conclusions

Summarize main findings and outline next steps.

---

# 9. Reproducibility Checklist

- Instructions to rerun this notebook
- Environment/dependencies
- Random seeds/configuration
- Data access

---

# 10. References

<!-- List references here or use a .bib file -->

---

# 11. Appendix (Optional)

Additional code, figures, or supplementary information.



# {{ cookiecutter.project_name }} - Notebooks

Project the notebooks. The naming convention is:
`[##.#]-[creator initials]-[short_description]-[yyyy_mm_dd].ipynb`

- `##.#` is the notebook number and version.
- `creator initials` are the initials of the person who created the notebook.
- `short_description` is a short `_` delimited description of the notebook,  .
- `yyyy_mm_dd` is the date the notebook was created.

Examples:
01-jrz-data_exploration-2024_10_02.ipynb
02.1-jrz_data_raw_analysis-2024_10_08.ipynb
02.2-jrz_data_raw_analysis-2024_11_21.ipynb

## folder structure

```bash
├── notebooks
│   ├── 01-data                   # data extraction and cleaning
│   ├── 02-exploration            # exploratory data analysis (EDA)
│   ├── 03-analysis               # Statistical analysis, hypothesis testing.
│   ├── 04-feat_eng               # feature engineering (creation, selection, and transformation.)
│   ├── 05-models                 # model training, evaluation, and hyperparameter tuning.
│   ├── 06-interpretation         # model interpretation
│   ├── 07-reports                # story telling, summaries and analysis conclusions.
│   ├── 08-deploy                 # model packaging, deployment strategies.
```

# Tracking experiments

01. Weights and Biases
02. Neptune
03. MLFlow



notebooks/
    ├── 01-data/
    │   ├── 11_data_extraction/
    │   ├── 12_data_loading/
    │   ├── 13_data_inspection/
    │   ├── 14_data_cleaning/
    │   ├── 15_data_validation/
    │   └── 16_data_saving/
    ├── 02-exploration/
    │   ├── 21_descriptive_statistics/
    │   ├── 22_univariate_analysis/
    │   ├── 23_bivariate_analysis/
    │   ├── 24_multivariate_analysis/
    │   ├── 25_outlier_detection/
    │   ├── 26_missing_value_analysis/
    │   └── 27_visualization/
    ├── 03-analysis/
    │   ├── 31_hypothesis_testing/
    │   ├── 32_correlation_analysis/
    │   ├── 33_group_comparison/
    │   ├── 34_time_series_analysis/
    │   └── 35_statistical_modeling/
    ├── 04-feat_eng/
    │   ├── 41_feature_creation/
    │   ├── 42_feature_transformation/
    │   ├── 43_feature_selection/
    │   ├── 44_feature_scaling/
    │   └── 45_dimensionality_reduction/
    ├── 05-models/
    │   ├── 51_baseline_models/
    │   ├── 52_advanced_models/
    │   ├── 53_hyperparameter_tuning/
    │   ├── 54_model_evaluation/
    │   └── 55_model_selection/
    ├── 06-interpretation/
    │   ├── 61_feature_importance/
    │   ├── 62_partial_dependence/
    │   ├── 63_shap_explainer/
    │   ├── 64_limitation_analysis/
    │   └── 65_domain_validation/
    ├── 07-reports/
    │   ├── 71_executive_summary/
    │   ├── 72_visual_storytelling/
    │   ├── 73_notebook_slides/
    │   └── 74_appendices/
    └── 08-deploy/
        ├── 81_model_packaging/
        ├── 82_api_deployment/
        ├── 83_dockerization/
        ├── 84_ci_cd_pipelines/
        └── 85_monitoring/
