---
title: "Workshop Presentation Template"
subtitle: "Interactive Training and Learning"
format:
  clean-revealjs:
    self-contained: true
    logo: "../../_extensions/SU_primary logo/RGB/Gold and maroon RGB/Png/SU corporate_horizontal_without_slogan_RGB-01.png"
    chalkboard: true
    multiplex: true
    overview: true
    touch: true
html-math-method:
  method: mathjax
  url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
author:
  - name: Instructor Name
    email: instructor@institution.edu
    affiliations: Your Institution
date: last-modified
brand:
  color:
    primary: "#61223b"
    secondary: "#b79962"
    tertiary: "#005F61"
  typography:
    fonts:
      - family: Montserrat
        source: google
      - family: Josefin Sans
        source: google
      - family: Fira Code
        source: google
    base: Montserrat
    headings:
      family: Josefin Sans
    monospace:
      family: Fira Code
---

# Welcome {background-color="#40666e"}

## Introduction

### Workshop Overview

- Welcome message
- Learning objectives
- Schedule and structure

### About the Instructor

- Background and expertise
- Contact information
- Resources and materials

## Pre-Workshop Assessment

### Quick Poll

:::: {.columns}
::: {.column width="70%"}
What is your experience level with this topic?

1. Beginner - completely new to this area
2. Intermediate - some familiarity but looking to improve
3. Advanced - experienced but seeking to expand knowledge
:::

::: {.column width="30%"}
Use your device to scan the QR code to participate in the poll
:::
::::

# Module 1: Fundamentals {background-color="#40666e"}

## Key Concepts

### Terminology

- Definition 1
- Definition 2
- Definition 3

### Framework

- Conceptual overview
- Practical applications
- Common challenges

## Demonstration

### Live Example

```{r}
#| echo: true
#| eval: false
# This is a code example
# It demonstrates a key concept
# Participants can follow along

example_function <- function(x) {
  # Process input
  result <- x * 2
  return(result)
}

example_function(5)
```

### Your Turn!

::: {.callout-note}
## Exercise 1
- Try modifying the example code to perform a different operation
- Share your results with a neighbor
- We'll discuss in 5 minutes
:::

# Module 2: Applications {background-color="#40666e"}

## Case Study

### Real-World Example

- Background of the case
- Challenges faced
- Approach taken

### Analysis

- Key insights
- Solutions implemented
- Results achieved

## Hands-On Activity

### Group Exercise

::: {.callout-important}
## Breakout Session (20 minutes)
1. Form groups of 3-4 people
2. Apply concepts from Module 1 to solve the provided problem
3. Prepare a brief explanation of your approach
4. Be ready to share with the larger group
:::

### Discussion

- What approaches did different groups take?
- What challenges did you encounter?
- How might this apply to your own work?

# Module 3: Advanced Topics {background-color="#40666e"}

## Advanced Techniques

### Building on Fundamentals

- Extension of basic concepts
- When to use advanced approaches
- Benefits and limitations

### Interactive Example

```{r}
#| echo: true
#| eval: false
# Advanced example code
# This demonstrates more complex functionality

advanced_function <- function(data, parameter) {
  # Complex processing
  result <- analyze(data, parameter)
  visualize(result)
  return(result)
}
```

## Best Practices

### Do's and Don'ts

:::: {.columns}
::: {.column width="50%"}
#### Recommended
- Best practice 1
- Best practice 2
- Best practice 3
:::

::: {.column width="50%"}
#### Avoid
- Common mistake 1
- Common mistake 2
- Common mistake 3
:::
::::

# Conclusion {background-color="#40666e"}

## Summary

### Key Takeaways

- Recap of main concepts
- Practical applications
- Resources for continued learning

### Q&A Session

- Open floor for questions
- Address specific use cases
- Clarify any points of confusion

## Next Steps

### Continuing Your Learning

- Additional resources
- Advanced workshops
- Community forums and support

### Feedback

- Please complete the workshop evaluation
- Your input helps improve future sessions

# Appendix {background-color="#40666e"}

## Reference Materials

### Additional Resources

- Books and articles
- Online courses
- Tools and software

### Code Repository

- Link to workshop materials
- Example code files
- Documentation
