---
title: "Academic Research Poster"
subtitle: "Research Findings and Analysis"
author:
  - name: "Author Name"
    affiliation: "Department, Institution"
    email: "author@institution.edu"
  - name: "Co-Author Name"
    affiliation: "Department, Institution"
    email: "coauthor@institution.edu"
date: last-modified
format:
  poster-typst:
    size: "48x36"
    poster-authors: "Author Name, Co-Author Name"
    departments: "Department, Institution"
    institution-logo: "../../styles/logo.png"
    institution-url: "institution.edu"
    footer-text: "Conference Name, Location, Date"
    footer-color: "#b79962"
    header-color: "#61223b"
    sectitle-color: "#61223b"
    columns: 3
    font-family: "Fira Sans"
    sectitle-font-family: "Fira Sans"
    fontsize: 30px
    sectitle-fontsize: 45px
    fontweight: light
    sectitle-fontweight: medium
    title-fontweight: regular
    title-fontsize: 65px
    sectitle-space-before: 0.5em
    sectitle-space-after: 0.2em
    sectitle-style: normal
    self-contained: true
bibliography: ../../references.bib
---

# Introduction

## Background

- [Brief context for your research]
- [Identify key gaps or challenges in the field]
- [Significance of addressing this research question]

## Research Question

[Clearly state your primary research question or objective]

# Methods

## Study Design

- [Type of study: experimental, observational, etc.]
- [Key methodological approaches]
- [Sample size and selection criteria]

## Data Collection

- [How data was collected]
- [Instruments or measures used]
- [Time period of data collection]

## Analysis

- [Statistical methods]
- [Software used]
- [Analytical approach]

# Results

## Key Finding 1

[Clearly state the first major finding]

```{r}
#| echo: false
#| fig-width: 8
#| fig-height: 6
#| fig-cap: "Figure 1: Caption describing the visualization"
# Insert visualization code here
plot(1:10, 1:10, type="l", xlab="X", ylab="Y")
```

## Key Finding 2

[Clearly state the second major finding]

```{r}
#| echo: false
#| fig-width: 8
#| fig-height: 6
#| fig-cap: "Figure 2: Caption describing the visualization"
# Insert visualization code here
plot(10:1, 1:10, type="l", xlab="X", ylab="Y")
```

## Statistical Results

[Summary of statistical analyses]

```{r}
#| echo: false
#| tbl-cap: "Table 1: Statistical Results"
# Insert table generation code here
data.frame(
  Variable = c("Var1", "Var2", "Var3"),
  Coefficient = c(0.45, -0.21, 0.33),
  "p-value" = c("<0.001", "0.04", "0.01")
)
```

# Discussion

## Interpretation

- [What do these findings mean?]
- [How do they relate to previous work?]
- [Theoretical or practical implications]

## Limitations

- [Acknowledge key limitations]
- [How might these affect the interpretation of results?]

# Conclusion

## Summary

- [Restate key findings]
- [Emphasize main contribution to the field]

## Future Directions

- [Suggest next steps for research]
- [Potential applications]

# References

::: {#refs}
:::

# Acknowledgments

[Funding sources]  
[Contributors]  
[Institutional support]

# Contact Information

**Author Name**  
Email: author@institution.edu  
Website: institution.edu/author

```{r qrcode, echo=FALSE}
#| eval: false
#| echo: false
# Uncomment to add QR code to website/paper
#library(qrcode)
#qr <- qr_code("https://yourwebsite.com/paper")
#plot(qr)
```
